A Higher-Order Approach to Explicit Contexts in LF

### 2015-03-08 paper/paper.tex
wordsmithing

  Another technique advanced by Krary is to represent contexts explicitly, and
  then define a sequent judgement over them; this can be used to resolve the
  problem described above (and several others), but it comes at the cost of
  verbosity, and cannot be to encode \emph{telescopes}, which are contexts
  where each successive term has the previous bound variables free in it.  In
  this paper, I demonstrate a higher-order encoding of contexts and telescopes
  which can be used to faithfully encode the sequent judgement for MLTT~1979.
\end{abstract}

@@

\section{Encoding Functional Hypothetico-General Judgement}
Henceforth I shall use the term ``sequent judgement'' to mean a
hypothetico-general judgement which also requires functionality. First, before
we get to the sequent judgement, we will need the concept of an ``open
categorical judgement''; this is a judgement which has variables from a
telescope free in it.

>>>>

  Another technique advanced by Krary is to represent contexts explicitly, and
  then define a sequent judgement over them; this can be used to resolve the
  problem described above (and several others), but it comes at the cost of
  verbosity, and introduces difficulties when used to encode \emph{telescopes}
  in the LF, which are contexts where where each successive term has the
  previous bound variables free in it.  In this paper, I demonstrate a
  higher-order encoding of telescopes which can be used to faithfully encode
  the functional sequent judgement for MLTT~1979.

\end{abstract}

@@

\section{Encoding Functional Hypothetico-General Judgement}
Henceforth I shall use the term ``functional sequent judgement'' to mean a
hypothetico-general judgement which also requires functionality. First, before
we get to the functional sequent judgement, we will need the concept of an ``open
categorical judgement''; this is a judgement which has variables from a
telescope free in it.
